\mytitle

### 2017-10-27 paper.tex
nits

% \documentclass[10pt]{sosp2015}
% \documentclass[10pt,onecolumn]{sosp2015}
\documentclass[10pt,onecolumn,letterpaper]{article}
% \usepackage[10pt,inchmargins]{sigmin}  %% template from Xi Wang.
%\special{papersize=8.5in,11in}
%\setlength{\pdfpagewidth}{8.5in}
%\setlength{\pdfpageheight}{11in}
\usepackage[noheadfoot,
	      left=1in,right=1in,top=1in,bottom=1in,
             columnsep=0.3in
             ]{geometry}
\usepackage[small,compact]{titlesec}
\usepackage[font={small,bf}]{caption}    % added 9/10/13
\usepackage[nolineno,noindent,norules]{lgrind}
\usepackage{tightenum}
\usepackage{float}
\usepackage{xspace}
\usepackage{times,pifont}
\usepackage{mathptmx}
\usepackage{subfig,graphics,graphicx,color}
\usepackage{multirow}
\usepackage{dblfloatfix} %% correctly orders single- and double-col figures
\usepackage{hyphenat}
\usepackage{mathrsfs}
\usepackage{subfig}
\usepackage{amssymb,amsmath,centernot}
\usepackage{lastpage}
\usepackage{flushend}
\usepackage{hhline}
\usepackage{authblk}
%\newcommand{\doi}{XXXXXX}

@@

\newcommand{\xxx}[0]{\textsc{Crane}\xspace}
\newcommand{\paxos}[0]{\textsc{Paxos}\xspace}
\newcommand{\mytitle}[0]{\textbf {Study Report}}
\newcommand{\mykeywords}[0]{State Machine Replication, Fault Tolerance, Stable 
and Deterministic Multithreading, Software Reliability}

@@

\newcommand{\apache}{\v{Apache}\xspace}
\newcommand{\mongoose}[0]{\v{Mongoose}\xspace}
\newcommand{\ab}{\v{ApacheBench}\xspace}
\newcommand{\clamav}{\v{ClamAV}\xspace}
\newcommand{\upnp}{uPnP\xspace}
\newcommand{\mediatomb}{\v{MediaTomb}\xspace}
\newcommand{\mencoder}{\v{mencoder}\xspace}
\newcommand{\mongodb}{\v{MongoDB}\xspace}
\newcommand{\ssdb}{\v{SSDB}\xspace}
\newcommand{\mysql}{\v{MySQL}\xspace}
\newcommand{\sysbench}{\v{SysBench}\xspace}
\newcommand{\zookeeper}{\v{ZooKeeper}\xspace}

@@

The fault-tolerant benefit of \smr makes it particularly an attractive 
high-availability service for general server programs. Unfortunately, despite 
much effort, existing \smr systems are still hard to deploy, mainly due to two 
problems.

The first problem is performance. The consensus latency of \paxos protocols is 
notoriously high and unscalable~\cite{zookeeper,glendenning2011scalable}, 
incurring high 
performance overhead for server programs. A main reason is that messages of 
traditional TCP or UDP-based \paxos protocols have to go through software 
network layers in OS kernels. For efficiency, \paxos 
protocols typically take the Multi-Paxos approach~\cite{paxos:simple}: it 
assigns one replica as the ``leader'' to invoke consensus requests, and the 
other replicas as ``backups'' to agree on requests. To agree on an input, at 
least one round-trip time (RTT) is required between the leader and a backup. 
Given that a ping RTT in LAN typically takes hundreds of \us, and that the 
request processing time of key-value store servers (\eg, \redis) is at most 
hundreds of \us, existing \paxos protocols incur high overhead in the response 
time of server programs.

Worse, the consensus latency of extant consensus protocols is often 
\emph{scale-limited}: it increases drastically when the number of concurrent 
requests or replicas increases. For instance, 
Scatter~\cite{glendenning2011scalable} shows that the consensus latency of its 
\paxos protocol increases by 1.6X when the number of replicas increases from 3 
to 9.

\begin{figure*}[ht]
\begin{center}
\includegraphics{figures/paxos_latency}
\caption{{\em Consensus latency of four existing consensus protocols.} All four 
protocols ran a client with 24 concurrent connections. The Y axis is broken to 
fit in all protocols.}\label{fig:paxos_latency}
\end{center}
\end{figure*}

To quantify this bottleneck, we evaluated four traditional consensus 
protocols~\cite{zookeeper, spaxos:srds12, crane:sosp15, libpaxos} on 24-core 
hosts with 40Gbps network, and we spawned 24 concurrent consensus connections. 
As shown in Figure~\ref{fig:paxos_latency}, when changing the replica group 
size from 3 to 9, although network and CPUs were not saturated, the consensus 
latency of 3 protocols drastically increased by 105.4\% to 168.3\%, and 36.5\% 
to 63.7\% of the increase was in OS kernel.

When only one consensus connection 
was spawned, the latency increase on the number of replicas was more gentle.

@@

The second problem is that most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services, 
developers often have to rewrite their code to orchestrate server programs into 
the narrowly defined interfaces provided by these \smr systems. For instance, 
to leverage ZooKeeper~\cite{zookeeper}, developers have to shoehorn their 
programs into the file IO interface defined by ZooKeeper.

>>>>

% \documentclass[10pt]{sosp2015}
% \documentclass[10pt,onecolumn]{sosp2015}
\documentclass[10pt,onecolumn,letterpaper]{article}
% \usepackage[10pt,inchmargins]{sigmin}  %% template from Xi Wang.
%\special{papersize=8.5in,11in}
%\setlength{\pdfpagewidth}{8.5in}
%\setlength{\pdfpageheight}{11in}
\usepackage[noheadfoot,
	      left=1in,right=1in,top=1in,bottom=1in,
             columnsep=0.3in
             ]{geometry}
\usepackage[small,compact]{titlesec}
\usepackage[font={small,bf}]{caption}    % added 9/10/13
\usepackage[nolineno,noindent,norules]{lgrind}
\usepackage{tightenum}
\usepackage{float}
\usepackage{xspace}
\usepackage{times,pifont}
\usepackage{mathptmx}
\usepackage{subfig,graphics,graphicx,color}
\usepackage{multirow}
\usepackage{dblfloatfix} %% correctly orders single- and double-col figures
\usepackage{hyphenat}
\usepackage{mathrsfs}
\usepackage{subfig}
\usepackage{amssymb,amsmath,centernot}
\usepackage{lastpage}
\usepackage{flushend}
\usepackage{hhline}
\usepackage{authblk}
\usepackage{booktabs}
%\newcommand{\doi}{XXXXXX}

@@

\newcommand{\xxx}[0]{\textsc{APUS}\xspace}
\newcommand{\paxos}[0]{\textsc{Paxos}\xspace}
\newcommand{\mytitle}[0]{\textbf {Study Report}}
\newcommand{\mykeywords}[0]{State Machine Replication, Fault Tolerance, Stable 
and Deterministic Multithreading, Software Reliability}

@@

\newcommand{\apache}{\v{Apache}\xspace}
\newcommand{\mongoose}[0]{\v{Mongoose}\xspace}
\newcommand{\ab}{\v{ApacheBench}\xspace}
\newcommand{\clamav}{\v{ClamAV}\xspace}
\newcommand{\upnp}{uPnP\xspace}
\newcommand{\mediatomb}{\v{MediaTomb}\xspace}
\newcommand{\mencoder}{\v{mencoder}\xspace}
\newcommand{\mongodb}{\v{MongoDB}\xspace}
\newcommand{\ssdb}{\v{SSDB}\xspace}
\newcommand{\mysql}{\v{MySQL}\xspace}
\newcommand{\sysbench}{\v{SysBench}\xspace}
\newcommand{\zookeeper}{\v{ZooKeeper}\xspace}
\newcommand{\libpaxos}{libPaxos\xspace}
\newcommand{\spaxos}[0]{S-Paxos\xspace}
\newcommand{\crane}[0]{CRANE\xspace}

@@

The fault-tolerant benefit of \smr makes it particularly an attractive 
high-availability service for general server programs. Unfortunately, despite 
much effort, existing \smr systems are still hard to deploy, mainly due to 
three problems.

\textbf{High consensus latency.} The consensus latency of traditional \paxos 
protocols is notoriously high, incurring high performance overhead for server 
programs. A main reason is that messages of traditional TCP or UDP-based \paxos 
protocols have to go through OS kernel. For efficiency, \paxos protocols 
typically take the Multi-Paxos approach~\cite{paxos:simple}: it assigns one 
replica as the ``leader'' to invoke consensus requests, and the other replicas 
as ``backups'' to agree on requests. To agree on an input, at least one 
round-trip time (RTT) is required between the leader and a backup. Given that a 
ping RTT in LAN typically takes hundreds of \us, and that the request processing 
time of key-value store servers (\eg, \redis) is at most hundreds of \us, 
existing \paxos protocols incur high overhead in the response time of server 
programs.

\begin{figure*}[ht]
\begin{center}
\includegraphics{figures/paxos_latency}
\caption{{\em Consensus latency of four existing consensus protocols.} All four 
protocols ran a client with 24 concurrent connections.}\label{fig:paxos_latency}
\end{center}
\end{figure*}

\textbf{Poor scalability.} The consensus latency of extant consensus protocols 
is often \emph{scale-limited}: it increases drastically when the number of 
concurrent requests or replicas 
increases~\cite{zookeeper,glendenning2011scalable}.

To quantify this problem, we evaluated four traditional consensus 
protocols~\cite{zookeeper, spaxos:srds12, crane:sosp15, libpaxos} on 24-core 
hosts with 40Gbps network. For each protocol, we spawned 24 concurrent 
consensus connections. As shown in Figure~\ref{fig:paxos_latency}, when 
changing the replica group size from 3 to 9, the consensus latency of three 
traditional protocols increased almost linearly to the number of replicas except 
S-Paxos. S-Paxos batches requests from replicas and invokes consensus when the 
batch is full. More replicas can take shorter time to form a batch, so S-Paxos 
incurred a slightly better consensus latency with more replicas. Nevertheless, 
its latency was always over 600\us.

To find scalability bottlenecks in traditional protocols, we used only one 
client connection and broke down their consensus latency on leader 
(Table~\ref{tab:traditional-latency}). From 3 to 9 replicas, the consensus 
latency (the ``Latency'' column) of these protocols increased more gently than 
that on 24 concurrent connections. For instance, when the number of replicas 
increased from three to nine, ZooKeeper latency increased by 30.3\% with one 
connection; this latency increased by 168.3\% with 24 connections (Figure 1). 
This indicates that concurrent consensus requests are the major scalability 
bottleneck for these protocols.

\begin{table}[h]
\caption{{\em Performance breakdown of traditional protocols on leader
with only one connection.} The ``Proto-\#Rep" column is the protocol name 
and replica group size; ``Latency" is the consensus latency; ``First" 
is the latency of leader's first received consensus reply; ``Major" is the
latency of leader's consensus; ``Process" is leader's time spent in
processing all replies; and ``Sys" is leader's time spent in systems (OS
kernel, network stacks, and JVM) between the ``First" and ``Major" 
reply. Times are in \us.}
\label{tab:traditional-latency}
\centering
\begin{tabular}{lrrrrr}
\toprule
{\bf Proto-\#Rep} & {\bf Latency} & {\bf First} & {\bf Major} & {\bf
Process}
& {\bf Sys}\\
\midrule
\libpaxos-3 & 81.6 & 74.0  & 81.6 & 2.5 & 5.1\\
\libpaxos-9 & 208.3 & 145.0  & 208.3 & 12.0 & 51.3\\

\zookeeper-3 & 99.0 & 67.0  & 99.0 & 0.84 & 31.2\\
\zookeeper-9 & 129.0 & 76.0  & 128.0 & 3.6 & 49.4\\

\crane-3 & 78.0 & 69.0  & 69.0 & 13.0 & 0\\
\crane-9 & 148.0 & 83.0  & 142.0 & 30.0 & 35.0\\

\spaxos-3 & 865.1 & 846.0  & 846.0 & 20.0 & 0\\
\spaxos-9 & 739.1 & 545.0  & 731.0 & 35.0 & 159.1\\
\bottomrule
\end{tabular}
\end{table}

Specifically, three protocols had scalable latency on the arrival of their 
first consensus reply (the ``First'' column), which implies that network is not 
saturated. \libpaxos is an exception because its two-round protocol consumed 
much bandwidth. However, on the leader, there is a big gap between the arrival 
of the first consensus reply and the ``majority'' reply (the ``Major'' column). 
Given that the replies' CPU processing time was small (the ``Process'' column), 
we can see that various systems layers, including OS kernel, network 
libraries, and language runtimes (e.g., JVM), are another major scalable 
bottleneck (the ``Sys'' column).

@@

\textbf{Hard to use.} Most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services, 
developers often have to rewrite their code to orchestrate server programs into 
the narrowly defined interfaces provided by these \smr systems. For instance, 
to leverage ZooKeeper~\cite{zookeeper}, developers have to shoehorn their 
programs into the file IO interface defined by ZooKeeper.
